% ============================================================
%  SECTION 2 — PROJECT GOALS & HYPOTHESES
% ============================================================

\begin{frame}{Project Goals}
  \begin{enumerate}
    \item \textbf{Define objective function} for elastic energy storage
          performance within a fixed planar footprint
          ($100\times100\times3$\,mm).
    \item \textbf{Generate candidate structures} via:
          \begin{itemize}
            \item Manual baseline designs (straight, folded, serpentine, curved beams)
            \item Computational topology optimisation (SIMP method)
          \end{itemize}
    \item \textbf{Compare} force--displacement behaviour, energy storage
          $E_{\text{in}}$, energy release $E_{\text{out}}$, and efficiency
          $\eta$ across topologies.
    \item \textbf{Analyse} how topology affects load paths, deformation modes,
          and stiffness distribution.
  \end{enumerate}
\end{frame}

\note{%
  \begin{itemize}
    \item Five concrete deliverables. Footprint locked at
          $100\times100\times3$ mm so every comparison is
          apples-to-apples (same volume budget, same boundary box).
    \item Two design paths in parallel: hand-designed baselines
          (straight / folded / serpentine / curved) and SIMP-optimised
          layouts in Octave.
    \item PLA chosen for repeatable FDM printing; same spool, same
          slicer settings used across all samples to remove material
          variability.
    \item Measurement = $F$--$\delta$ curve under quasi-static
          loading; integrate to get $E_{\text{in}}$ / $E_{\text{out}}$,
          divide for $\eta$.
    \item Goal 5 is the science: link the measured $\eta$ back to
          where the strain actually went in each topology.
  \end{itemize}
}

\begin{frame}{Hypotheses}
  \begin{itemize}\setlength\itemsep{8pt}
    \item \textbf{H1 — Fold-count effect within a pattern family:}
          For a fixed planar footprint ($100\times100\times3$\,mm) and
          constant material volume, the elastic energy storage
          efficiency $\eta$ of a folded beam varies systematically
          with the \emph{number of folds} within a given pattern
          (e.g.\ a triangular wave with 1, 2, 3, \ldots\ folds; a
          square wave across multiple folds).

    \item \textbf{H2 — Topology optimisation:}
          Topology-optimised structures will outperform manually
          designed baselines in terms of energy efficiency and
          performance stability.
  \end{itemize}
\end{frame}

\note{%
  \begin{itemize}
    \item \textbf{H1 rationale:} more folds lengthen the effective
          load path inside the same footprint, distributing strain
          and delaying local yielding. But excessive folding
          concentrates stress at the corners of each fold. Expect a
          \emph{non-monotonic} optimum --- $\eta$ rises with fold
          count, peaks, then falls.
    \item Pattern family is the second axis: triangular vs.\ square
          wave at the same fold count gives different corner radii
          and different bending-vs-torsion mix. Both knobs swept.
    \item Volume held constant, not volume \emph{fraction} ---
          we add/remove fold count by changing geometry, not by
          changing how much PLA is in the box.
    \item \textbf{H2 rationale:} SIMP explores non-intuitive layouts
          that balance stiffness and compliance better than human
          intuition. Also expect lower trial-to-trial variance ---
          optimised geometry should be less sensitive to print
          defects because load is distributed.
    \item If H1 holds but H2 fails $\Rightarrow$ folded heuristic is
          already near-optimal. If both hold, SIMP wins on both
          mean $\eta$ and variance.
  \end{itemize}
}

\begin{frame}{Experimental Variables}
  \footnotesize
  \begin{tabularx}{\textwidth}{@{}p{2.0cm}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}X@{}}
    \toprule
     & \textbf{H1: Fold count / pattern}
     & \textbf{H2: Topology optimisation} \\
    \midrule
    \textbf{Independent}
      & Number of folds $n$\newline
        Pattern family\newline
        (triangular wave, square wave, \ldots)
      & Design method (manual baseline vs.\ SIMP-optimised) \\
    \addlinespace
    \textbf{Dependent}
      & $\eta$, $E_{\text{in}}$, $E_{\text{out}}$, stiffness $k$,
        peak force $F_{\max}$
      & $\eta$, $E_{\text{in}}$, $E_{\text{out}}$, stiffness $k$,
        trial-to-trial variance \\
    \addlinespace
    \textbf{Controlled}
      & Material volume\newline
        Footprint $100{\times}100{\times}3$\,mm\newline
        PLA + print parameters\newline
        Clamping BCs\newline
        Quasi-static loading rate
      & Volume fraction $f$\newline
        Footprint $100{\times}100{\times}3$\,mm\newline
        PLA + print parameters\newline
        Clamping BCs\newline
        Quasi-static loading rate \\
    \bottomrule
  \end{tabularx}
\end{frame}

\note{%
  \begin{itemize}
    \item Walk the table column by column so the audience sees H1
          and H2 share most variables and only diverge on the IV.
    \item Independent: H1 sweeps a geometric integer ($n$) and a
          pattern family; H2 swaps the design \emph{generator}
          (human vs.\ SIMP).
    \item Dependent: $\eta$, $E_{\text{in}}$, $E_{\text{out}}$, $k$
          identical between hypotheses --- enables direct
          cross-hypothesis comparison. H2 adds variance because the
          claim is partly about repeatability.
    \item Controlled: footprint, material, print settings, clamping,
          loading rate are locked. The only difference is what is
          held constant about the material:
          \begin{itemize}
            \item H1 fixes \emph{volume} (same gram of PLA, varied
                  geometry).
            \item H2 fixes \emph{volume fraction} (SIMP constraint
                  $f = V/V_0$).
          \end{itemize}
    \item Every sample printed from one PLA spool, same slicer
          profile, same orientation --- removes batch effects.
  \end{itemize}
}
